---
title: "predictionanalysis"
author: "Jennifer Sailor"
date: "2022-11-22"
output:
  pdf_document: default
  html_document: default
---

To run: must have run testing.R with all 65 people must have run demographics.Rmd

```{r}
(var <- table(as.numeric(prediction), as.matrix(test[,1])))
(var <- table(as.numeric(prediction), as.matrix(val[,1])))

```

How to read this: So it isn't for say not in numerical order because I checked both y and prediction which is what makes this matrix and they are in the correct order

So how to read this beast so if var2_ii is not 20 then check the full column where var2_ii != var2_ii and var2_ii != 0. Here will be var2_ki (row changes but column doesnt) and that k/row number will tell you who it is incorrectly predicting var2_ii as

```{r}
numberofpics <- 6 #the max number of pictures of an individual in data set

#PART 1
#finding total accuracy (used later), who was predicted wrong, and accuracy of those predicted wrong

#initiating variables
sum <- 0 #total sum of those predicted correctly - helps find total accuracy
wrong_pred <- c() #demographics of individual who is predicted incorrectly
accuracy_right_4wrong <- c() #the accuracy of individuals who were predicted incorrectly

#loop through table
for (i in 1:ncol(var)) {
  
  sum <- sum + var[i,i]#adding up total along diagonal
  
  #if the diagonal is not equal to number of pictures of individual
  #then atleast of the picture was predicted incorrectly
  if(var[i,i] != numberofpics){
    
    #since individual is predicted incorrectly add demographic 
    #information to data set corresponding to individuals name
    #to do this must loop through demographics data frame and find
    #where names math
    for(j in 1:nrow(demographics))
      #if the names match then add demographic information 
      #to the wrong pred matrix
      if(folders[i] == demographics[j,1]){
        wrong_pred <- rbind(wrong_pred, demographics[j,]) 
      }
    
    #since individual is incorrectly predicted
    #lets find percent that it was correct for individual
    accuracy_right_4wrong <- c(accuracy_right_4wrong, round(100*var[i,i]/(numberofpics), 2))
  }
}

#PART 2
#finding all names of wrong predictions that respond to individual

#making matrix that nxm where n is number of individuals predicted wrong and m is number of pictures incorrect
#this makes it so that each row corresponds to indivual is is predicted wrong and each column is the prediction
predname_wrong <- matrix(nrow = (nrow(wrong_pred)), ncol = (numberofpics-(min(accuracy_right_4wrong)/100*numberofpics)))

#initializing variables that will help know where to add in matrix
colofmat <- 0 #column of matrix
rowofmat<-0 #row of matrix

#loop through table
for (i in 1:ncol(var)) {

  #if the diagonal is not equal to number of pictures of individual
  #then at least of the picture was predicted incorrectly 
  if(var[i,i] != numberofpics){
    #individual was predicted incorrectly atleast once
    
    colofmat <- colofmat+1 #add one to column
    
    #loop that goes from 1 to number of individuals/which is the number of rows in var
    for(k in 1:8){
      #in the column of the the incorrect prediction lets find the who was predicted instead
      #thus where is column not 0 and not the diagonal position
      if(var[k,i] != 0 && k != i){
        #at this position the value was predicted incorrectly and the value of var[k,i] is 
        #how many times it was predicted this person so we do a for loop up to that value
        for(s in 1:var[k,i]){
          rowofmat <- rowofmat +1#add one to the row
          
          #put the name of incorrect prediction into the matrix
          predname_wrong[colofmat,rowofmat] <- folders[k]
        }
      }
    }
  
    rowofmat <- 0#resetting the row index to 0
    
  }
  
}

#PART 3
#used later
#finding a list of all the incorrect predictions (probably a more efficient way using var)

#intialize a empty list
listofnameswrong <- c()

#for loop that goes from 1 to the length of the list of predictions (could use length of y but it is the same)
for(i in 1:length(as.numeric(prediction))){
  #if the prediction does not match the matrix this add the name of prediction to list of wrong predictions
  if(as.numeric(prediction)[i] != as.matrix(y)[i]){
    listofnameswrong <- c(listofnameswrong, folders[as.numeric(prediction)[i]])
  }
}

#PART 4 
#make data frame
#this just combines parts 1 and 2 into a pretty dataframe to analyze
incorrectresults <- data.frame(cbind(wrong_pred, accuracy_right_4wrong, predname_wrong))
colnames(incorrectresults)[4] <- "Accuracy (%)"
colnames(incorrectresults)[5] <- "Predicted individual as..."
incorrectresults[,-3]
```

```{r}
#Analysis of above datafram of incorrect results
paste0("Total Accuracy of the algorithm ", round(100*sum/(numberofpics*8), 2), "%")
paste0("The name that was predicted the most as someone else was ", max(listofnameswrong), " with a count of ", sum(listofnameswrong == max(listofnameswrong)))
paste0("The highest number of inaccurate predictions per person was: ", numberofpics-(min(accuracy_right_4wrong)/100*numberofpics))
#paste0(round(100*sum(incorrectresults$gender == "M")/sum(demographics$gender == "M"),2),"% of the men were detected inaccurately") # (12/52)
#paste0(round(100*sum(incorrectresults$gender == "F")/sum(demographics$gender == "F"),2), "% of the women were detected inaccurately") #(4/13)

```



